Wind Veer and Speed in Turbulent Ekman Flow Part I: Scaling analysis and universal profile model

### 2024-10-31 write1/manuscript.tex
added affiliation for Hauke

\date{\scriptsize Submitted \today}
\title{Wind Veer and Speed in Turbulent Ekman Flow - Part 1: Scaling analysis and universal profile model}
\titlerunning{A Universal Velocity Profile for Ekman Flow}
\author{Cedrick Ansorge$^1$ and Hauke Wurps$^2$}
\authorrunning{C Ansorge and H Wurps}
\institute{$^{1}$\,FU Berlin, Institut f\"ur Meteorologie, Carl-Heinrich-Becker-Weg 6--10, 12165 Berlin {cedrick@posteo.de}\\
  $^{2}$\,Uni Oldenburg 
  }

>>>>

\date{\scriptsize Submitted \today}
\title{Wind Veer and Speed in Turbulent Ekman Flow Part I: Scaling analysis and universal profile model}
\titlerunning{A Universal Velocity Profile for Ekman Flow}
\author{Cedrick Ansorge$^1$ and Hauke Wurps$^{2,3}$}
\authorrunning{C Ansorge and H Wurps}
\institute{$^{1}$\,FU Berlin, Institut f\"ur Meteorologie, Carl-Heinrich-Becker-Weg 6--10, 12165 Berlin, Germany {cedrick@posteo.de}\\
  $^{2}$\,Carl von Ossietzky Universit\"at Oldenburg, School of Mathematics and Science, Institute of Physics \\ 
  $^{3}$\,ForWind - Center for Wind Energy Research, K\"upkersweg 70, 26129 Oldenburg, Germany 
  }
